Distributed Tic Tac Toe:\\ Peer-to-Peer Team-Based Gaming System

### 2017-12-01 paper/paper.tex
added texttt labels to a few places

These failures were all caused by \texttt{java.rmi.ConnectException}, which was thrown in response to refused TCP connections. Java RMI calls require an exclusive TCP connection to a client, which is not suited to the ``Bully'' algorithm. Although a new leader is still elected from the suriving nodes, these failures strongly suggest that modifying RMI to use UDP sockets or \texttt{SO\_REUSEADDR}-enabled TCP sockets is required for a more failure-resistant system. This idea is covered in more detail below in Architecture Evaluation.

The next step would be to repeat these tests in a scenario closer to how this project is likely to be used in an educational setting such as a university lab exercise: several different machines each running between one and three instances of the game. We would record how many failures are caused by \texttt{java.rmi.ConnectException} in comparison to running all instances on \texttt{localhost} as well as comparing the average time taken to process votes.

@@

Hole punching for NAT traversal requires the use of an external, publicly-accessible proxy server to distribute the public-facing IP address and port combinations (addr:port) of NAT-obscured clients which want to establish a peer-to-peer session. This traversal method is used by many popular types of distributed applications such as multiplayer gaming, VoIP, and peer-to-peer file sharing. This technique takes advantage of the behaviour of NAT middleboxes to create and maintain an 'open' addr:port combination - without this, a fully decentralised peer-to-peer session cannot be established.

As mentioned above, Java RMI uses TCP for its operations by default. While it is possible to modify the sockets created by RMI calls to use UDP instead, this requires extensive work using RMISocketFactory which is beyond the time allowed by the project.

>>>>

These failures were all caused by \texttt{java.rmi.ConnectException}, which was thrown in response to refused TCP connections. Java RMI calls require an exclusive TCP connection to a client, which is not suited to the ``Bully'' algorithm. Although the election algorithm itself is resilient and still elects a new leader from the surviving nodes, these failures strongly suggest that modifying RMI to use UDP sockets or \texttt{SO\_REUSEADDR}-enabled TCP sockets is required for a more failure-resistant peer-to-peer system. This idea is covered in more detail below in Architecture Evaluation.

The next step would be to repeat these tests in a scenario closer to how this project is likely to be used in an educational setting such as a university lab exercise: several different machines each running between one and three instances of the game. We would record how many failures are caused by \texttt{java.rmi.ConnectException} in comparison to running all instances on \texttt{localhost} as well as comparing any difference in average time taken to process votes.

@@

Hole punching for NAT traversal requires the use of an external, publicly-accessible proxy server to distribute the public-facing IP address and port combinations (\texttt{addr:port}) of NAT-obscured clients which want to establish a peer-to-peer session. This traversal method is used by many popular types of distributed applications such as multiplayer gaming, VoIP, and peer-to-peer file sharing. This technique takes advantage of the behaviour of NAT middleboxes to create and maintain an 'open' addr:port combination - without this, a fully decentralised peer-to-peer session cannot be established.

As mentioned above, Java RMI uses TCP for its operations by default. While it is possible to modify the sockets created by RMI calls to use UDP instead, this requires extensive work using \texttt{RMISocketFactory} which is beyond the time allowed by the project.
